Motorcycle Acceleration example

### 2018-11-06 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

```{r load-pkgs, message=FALSE}
library(MASS)
library(lattice)
library(smashr)
library(wavethresh)
library(EbayesThresh)
source("../code/motorcycle.functions.R")
```

Note that the MASS and lattice packages are included in most standard
R installations.

>>>>

```{r load-pkgs, message=FALSE}
library(MASS)
library(scales)
library(lattice)
library(smashr)
library(wavethresh)
library(EbayesThresh)
source("../code/motorcycle.functions.R")
```

Note that the MASS and lattice packages are included in most standard
R installations, so you probably don't need to install these packages
separately.
